We are not the 99 percent: quantifying asphericity in the Local Group satellites' distributions

### 2017-11-03 paper/paper.tex
remove mu information

It has been shown that LG pair separation vector is aligned along the
filaments in  which they are typically embeded
\citep{2015ApJ...799...45F}, the LG pairs found in pancake-like DM
matter arrangements are aligned with the plane itself. 
Characterizing the satellite alignments with $\mu$ thus provide
information about how satellites are distributed with respect to the
cosmic web. 
For that reason we also characterize the alignment between the satellite plane and the
vector connecting the two dominant galaxies by $\mu=|\hat{r}_{AB}\cdot
\hat{n}|$.

To summarize we characterize the satellite distribution by for
quantities obtained from the inertia tensor: 
\begin{itemize}
\item Plane width, $w$.
\item $c/a$ axis ratio.
\item $b/a$ axis ratio.
\item $\mu$ as a measure of plane alignment.
\end{itemize}

@@

We compare every satellite distribution against its own spherically
randomized distribution.
We keep fixed the radial position of every satellite
with respect to the central galaxy and then randomizing its angular
position. 
We repeat this procedure 1000 times for each satellite distribution
and proceed to measure the quantities mentioned in the last section:
$w$, $c/a$, $b/a$ and $\mu$.
For each quantity we compute an average and standard deviation from
the 1000 random samples. 
This allows us to build a normalized version of all quantities of
interest by substracting the mean and dividing between the standard
deviation of the randomized samples.

@@

After building the normalized variables with the simulated data we
perform  a Kolmogorov-Smirnov test with the null hypothesis of belongig
to a normal distribution with mean and standard deviation computed
from the mean and standard deviation from the data itself. 
We find that the distributions for $w$, $c/a$ and $b/a$ cannot reject
the null hypothesis. 
Only the distribution for $\mu$ corresponds to a
uniform distribution.

@@

\begin{figure*}
\centering
\includegraphics[width=0.32\textwidth]{scatter_random_ranked_mu.pdf}
\includegraphics[width=0.32\textwidth]{scatter_ranked_mu.pdf}
\includegraphics[width=0.32\textwidth]{scatter_norm_ranked_mu.pdf}
\caption{Same layout as in Figure \ref{fig:scatter_width}. 
This time for $\mu$ the absolute value of the dot product between the
vector connecting the main galaxies and the vector perpendicular to
the satellite plane.
In this case both the MW and M31 show a strong alignment.
Apparently the LG is outside the expectations from
simulations and atypical compared to the spherical results. 
However, this is not the case. The $\mu$ distributions in the
randomization and the simulation are consistent with a uniform
distribution.
Under such circumstances $\mu\approx 1$ is as likely as
any other value.
\label{fig:scatter_mu}}
\end{figure*}

@@

\subsection{Plane alignment}

Figure \ref{fig:scatter_mu} summarizes the Illustris results for the
alignments between the vector normal to the plane and the vector
connecting the two dominant galaxies.
The corresponding results for the ELVIS data are shown in Figure
\ref{fig:scatter_elvis}.

The first striking impression from the left panel in Figure
\ref{fig:scatter_mu} is that the observations are cornered in
a region of strong alignment, $\mu\approx 1$, for both galaxies. 
In other words, the planes are almost perpendicular to the direction
connecting the two galaxies. 
The result for the spherical randomization corresponds to a uniform
distribution $0\leq \mu\leq 1$ as shown in the same panel.

The middle panel tells a similar story for the results from
Illustris. That is, there isn't a prefered alignment direction from
the simulation. This also holds for ELVIS data.
We quantify this visual impresion by performing a K-S test where the
null hypothesis corresponds to an uniform distribution. 
The results from the K-S test do not allow us to discard the null
hypotesis.

This information allows us to properly understand the results on the
right panel in Figure \ref{fig:scatter_mu}.
That panel shows the results for the normalized values to the mean and
standard deviation computed from spherically randomized
ditributions.
In this case the LG $\mu$ value has the same probability as any other value
(because it is consistent with an uniform distribution) and the apparent
large distance from the Illustris data must not be interpreted as an
the LG having an atypical alignment.

We defer to the Section \ref{sec:discussion} our discussion on how
this can be reconciled with other studies that show preferential
infall satellite directions in LCDM simulations.

>>>>

To summarize we characterize the satellite distribution by for
quantities obtained from the inertia tensor: 
\begin{itemize}
\item Plane width, $w$.
\item $c/a$ axis ratio.
\item $b/a$ axis ratio.
\end{itemize}

@@

We compare every satellite distribution against its own spherically
randomized distribution.
We keep fixed the radial position of every satellite
with respect to the central galaxy and then randomizing its angular
position. 
We repeat this procedure 1000 times for each satellite distribution
and proceed to measure the quantities mentioned in the last section:
$w$, $c/a$ and $b/a$.
For each quantity we compute an average and standard deviation from
the 1000 random samples. 
This allows us to build a normalized version of all quantities of
interest by substracting the mean and dividing between the standard
deviation of the randomized samples.

@@

After building the normalized variables with the simulated data we
perform  a Kolmogorov-Smirnov test with the null hypothesis of belongig
to a normal distribution with mean and standard deviation computed
from the mean and standard deviation from the data itself. 
We find that the distributions for $w$, $c/a$ and $b/a$ cannot reject
the null hypothesis.

@@

@@
